Domain Specific Language for high performance computing

### 2024-01-05 paper/paper.tex
laptop 20240105

% \documentclass[ams]{U-AizuGT}
\documentclass{jarticle}
% \usepackage{pifont}
% \usepackage{graphicx}
% \usepackage{cite}

\bibliographystyle{ieice}

\author{Ryuki Hiwada}
% \studentid{s1280076}
% \supervisor{Naohito Nakasato}
\title{Domain Specific Language for high performance computing}
\begin{document}
\maketitle
\section{Introduction}
test
\section{Abstruct}
\section{Conclusion}
\section{Acknowledgement}
\bibliography{biblist}

\end{document}

>>>>

% \documentclass[ams]{U-AizuGT}
\documentclass[twocolumn, a4j]{article}
% \usepackage{pifont}
% \usepackage{graphicx}
% \usepackage{cite}

% \twocolumn[
\bibliographystyle{ieice}
\author{Ryuki Hiwada}
% \studentid{s1280076}
% \supervisor{Naohito Nakasato}
% ]
\title{Domain Specific Language for high performance computing}
\begin{document}
\maketitle
\section{Abstract}
\section{Introduction}
\subsection{Background}
In astrophysics and astronomy, to numerically calculate the dynamical 
evolution of N particles interacting gravitationally, N-body simulations 
are required. Figure 1 shows the equation for interparticle interactions 
in N-body simulations. If the equation is naively computed, the time
complexity of calculation of interparticle interactions is 
\begin{math}O(N^2) \end{math}, where 
N is the number of particles. Therefore, parallelization is required to
speed up numerical simulations. To write a parallelized code for a 
numerical simulation, a user needs to understand the architecture of 
computer systems in  detail. If a parallelized code is automatically
generated by only describing the formulas and data of the numerical
simulation, the above problems are solved. To realize the parallelization,
we will develop Domain Specific Language \lparen DSL \rparen, which is a 
programming language specialized to a domain, for example, SQL and HTML.
\subsection{implemented DSL}

\subsection{parallelization}

\subsection{Aim of this paper}

\section{Method}
\subsection{Use Sympy for DSL development.}

\section{Conclusion}
\section{Acknowledgement}
\bibliography{biblist}
\end{document}
